```{r, child = "_setup.Rmd"}
```

# Centering elements

Center an input above a larger element or next to the element if space allows.

```{r}
div(
  .style %>%
    flex_display() %>%
    flex_direction("column", md = "row"),

  radioButtons("rb1", "Radios", c("Choice 1", "Choice 2")) %>%
    margin_horizontal("auto", md = 0),

  div(
    .style %>%
      width(100) %>%
      background_color("primary") %>%
      text_color("white"),
    "Placeholder"
  )
)
```

# Details

This section needs pretty specific examples of how to use flex. I don't know
that people will want a tutorial on flex.

For the sake of the demo let's create a flex item help function.

```{r}
flexItem <- function(...) {
  div(
    .style %>%
      padding(3) %>%
      border_color("primary"),
    "A flex item",
    ...
  )
}
```

## Different `direction`s

Many of `flex()`'s arguments are viewport responsive. On small screens the flex
items are placed vertically and can occupy the full width of the mobile
device. On medium or larger screens the items are placed horizontally.

```{r}
div(
  .style %>%
    flex_display() %>%
    flex_direction("column", md = "row"),
  flexItem(),
  flexItem(),
  flexItem()
)
```

*Resize the browser for this example.*

You can keep items as a column by specifying only `"column"`.

```{r}
div(
  .style %>%
    flex_display() %>%
    flex_direction("column"),  # <-
  flexItem(),
  flexItem(),
  flexItem()
)
```

## Spacing items with `justify`

Below is a series of examples showing how to change the horizontal alignment of
your flex items. Let's start by pushing items to the beginning of their parent
container.

```{r}
div(
  .style %>%
    flex_display() %>%
    flex_justify("start"),  # <-
  flexItem(),
  flexItem(),
  flexItem(),
  flexItem()
)
```

We can also push items to the **end**.

```{r}
div(
  .style %>%
    flex_display() %>%
    flex_justify("end"),  # <-
  flexItem(),
  flexItem(),
  flexItem(),
  flexItem()
)
```

Without using a table layout we can **center** items.

```{r}
div(
  .style %>%
    flex_display() %>%
    flex_justify("center"),  # <-
  flexItem(),
  flexItem(),
  flexItem(),
  flexItem()
)
```

You can also put space **between** items

```{r}
div(
  .style %>%
    display("flex") %>%
    flex(justify = "between"),  # <-
  flexItem(),
  flexItem(),
  flexItem(),
  flexItem()
)
```

... or put space **around** items.

```{r}
div(
  .style %>%
    flex_display() %>%
    flex_justify("around"),  # <-
  flexItem(),
  flexItem(),
  flexItem(),
  flexItem()
)
```

The `"between"` and `"around"` values come from the original CSS values
`"space-between"` and `"space-around"`.

## `wrap` onto new lines

Using flexbox we can also control how items wrap onto new lines.

```{r}
div(
  .style %>%
    flex_display() %>%
    flex_wrap(),
  flexItem(),
  flexItem(),
  flexItem(),
  flexItem(),
  flexItem(),
  flexItem()
)
```
